---
title: "Student Sit In"
author: "Ariana Rodriguez"
date: "28 October 2019"
output: 
  html_document:
    toc: true
    number_sectons: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ONE SHOT assignment!
this is an extra credit assignment, must be completed Monday Oct 28, turn-in closes at midnight!

## Problem statement: 
Students at UCD- is there a relation between where one sits and one's major? 

## Introduction  

<!-- where is the data found?  Is this an experiment or an observational study?  !-->

Data from this study came from UC Davis and it is an obseravtional study.  



```{r include=FALSE, echo=FALSE}
library(tigerstats)
data(ucdavis1)

```

$H_0$: there is no relationship between one's major and where one sits in a class   
$H_A$: where one sits in class and one's major are related  

<!-- Get the data: !-->

names of the data in the data frame are seat and major

```{r echo=FALSE}
UCDdataframe = data.frame(seat=ucdavis1$Seat, major=ucdavis1$class, data=ucdavis1)
names(UCDdataframe)
```
## Methods

<!--  describe analysis methods here 
what are the variable types, and indicate gaphical, numerical, and inferential methods appropriate
for this question  !--> 

The variables in this analysis are both categorical therefore bar graphs and tables are used for the data and a chisquare test is used for the inferential results. 

## Data summary

**Graphical summary**

```{r}
barchartGC(~seat+major, data=UCDdataframe, main='Seat & Major' , type='Percent', xlab='Seat')
```

This graph shows that students with a LibArts major tend to sit more towards the front of a class rather than the back, and students with a NonLib major sit relatively anywhere. 


**Numerical summary**

```{r}
tab1 = xtabs(~seat+major, data=UCDdataframe)
rowPerc(tab1)
```

The numerical summary says that students with a LibArts major tend to sit more towards the front of a class rather than the back, and students with a NonLib major sit relatively anywhere. 

## Inferential Results

```{r}
chisqtestGC(tab1)
```

The p-value of the chisquare test is 0.2173

## Results and conclusions

<!-- explain-- is there evidence that certain majors tend to sit in particular areas of the class?  Can the results of this test be generalized to all majors in all universities? !-->

The p-value for the chisquare test is 0.2173 which is greater than 0.05 therefore we fai to reject the null hypthesis that there is a relation between one's major and where one sits in class. 

<!--
push results to your github account, turn in the URL

--OR--

If you did not fork my repo to your github account,
create a repository in your github account for this project, get the URL for that repo and 
(in the terminal window..)

$git remote add origin URL_of_your_github_repo
$git push -u origin master

!-->